Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
add chi square
Add reference

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies}. [NEED REF]  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
{\bf However,} this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1883$	& $-0.1813$  \\
$y_1$	  &$-0.1923$	&$-0.1695$  \\
$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
$y_2$	  &$-0.2502$	& $-0.1843$  \\
$\sigma_1$ &$141.3$     & $144.9$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.5$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
\end{tabular}

@@

Additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy.  These systems will be investigated in
future work, but the images alone strongly suggest that other lens
systems have similar links between flux-ratio anomalies and disk
components.  Although the number of radio loud flux anomalous lensed
quasars remains small, a new technique using narrow-line emission
regions will enlarge the sample and bring statistical perspective on
substructures in the near future \citep{N14}. It is well known (e.g,
Kochanek 199??) that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies. Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}. Otherwise, derived
substructure fractions should be considered as upper limits.

>>>>

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies} \citep{DES15,Kop15}.  
This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
{\bf However,} this process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens models.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	  & $-0.1883$	& $-0.1813$  \\
$y_1$	  &$-0.1923$	&$-0.1695$  \\
$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
$y_2$	  &$-0.2502$	& $-0.1843$  \\
$\sigma_1$ &$141.3$     & $144.9$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.5$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
$\chi ^2$ & $1.05$ & $0.04$ \\
\hline
\end{tabular}

@@

Additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy.  These systems will be investigated in
future work, but the images alone strongly suggest that other lens
systems have similar links between flux-ratio anomalies and disk
components.  Although the number of radio loud flux anomalous lensed
quasars remains small, a new technique using narrow-line emission
regions will enlarge the sample and bring statistical perspective on
substructures in the near future \citep{N14}. It is well known (e.g,
\citep{Ka91}) that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies. Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}. Otherwise, derived
substructure fractions should be considered as upper limits.
